\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-12-31 paper.Rmd
JSS submission

```{r setup, include=FALSE}
require(knitr)
require(shorts)
require(tidyverse)
require(bookdown)
require(magick)

pdf2png <- function(path) {
  # only do the conversion for non-LaTeX output
  if (knitr::is_latex_output()) 
    return(path)
  path2 <- xfun::with_ext(path, "png")
  img <- magick::image_read_pdf(path)
  magick::image_write(img, path2, format = "png")
  path2
}

@@

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 600,
  dev = "png",
  fig.process = pdf2png,
  out.width = "100%",
  fig.align = "center",
  fig.width = 6,
  fig.height = 6 * 0.618, # 1 / phi
  fig.show = "hold",
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  width = 70
)

>>>>

```{r setup, include=FALSE}
require(knitr)
require(shorts)
require(tidyverse)
require(bookdown)

@@

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "100%",
  fig.align = "center",
  fig.width = 6,
  fig.height = 6 * 0.618, # 1 / phi
  fig.show = "hold",
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  width = 70
)
